\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-21 submission/manuscript.Rmd
discussion

<!-- inter-indiv correlates -->
Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with stronger narcissism (in particular the acclaim seeking and grandiose fantasies dimensions) displayed a stronger confidence in their simulation monitoring judgments. This is in line with the literature

While early researchers had proposed narcissism to be a unitary construct [@raskin1988principal; @sedikides2004normal], recent studies cast narcissism as encompassing 2 unique dimensions - namely narcissistic vulnerability, which is characterized by low self-esteem and a need for admiration, and narcissistic grandiosity, which encompasses high self-esteem, arrogance and aggressive self-assertiveness [@pincus2011narcissistic]. Whereas narcissism has long been linked to over-confidence in decision-making [@campbell2004narcissism], a growing body of research indicates that this relationship is likely mostly driven by facets of narcissistic grandiosity (such as Acclaim Seeking), which drives individuals to see themselves as more superior than others and to externalize blame for poor decision-making consequences [@o2021grandiose]. Indeed, the evidence alludes that attributes specific to narcissistic grandiosity predict individuals' overconfidence in cognitive decision-making [@chatterjee2017master; @brunell2017narcissism; @o2021grandiose].

Conversely, the literature on the correlation between honesty-humility and perceptual confidence judgements remain comparatively scarce, albeit some existing research links higher levels of honesty-humility to increased perceptions of risk and greater risk aversion [@levidi2022understanding; @weller2012honest]. As such, it could be argued that individuals with higher levels of honesty-humility could inherently possess a greater simulation monitoring sensitivity, perceiving a higher risk involved in making decisions on realness and therefore be less confident of their beliefs of reality. This is further supported by convergent evidence finding a negative link between honesty-humility and narcissism [@hodson2018dark]. Therefore, further research examining the relationship between simulation monitoring decisions, personality traits, particularly that related to the dark triad and honesty-humility, and the perceived risks involved in making such evaluations, is warranted.

<!-- AI attitudes -->
Interestingly, despite the ubiquity of AI, there is a lack of research pertaining to the influence of people's AI attitudes on their confidence in their discriminative ability to distinguish between output that is "true" (i.e., images of real faces) from those that is artificially-generated. One possible explanation for the positive relationship observed between AI-Enthusiasm and confidence in reality judgements could be that individuals with highly positive AI attitudes may perceive themselves as having greater knowledge about AI and its capabilities, hence permitting them to be more confident in their simulation monitoring decisions. This is in line with previous research findings, which indicate that greater enthusiasm about AI is related to having a higher confidence in one's knowledge regarding AI competencies [@said2022artificial]. Moreover, @said2022artificial further reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications. Specifically, people with AI attitudes that were highly positive and that were more confident in their AI knowledge were more likely to over-estimate the advantages of AI and under-estimate the risks involved in their application. As such, it is plausible that individuals' perceived self-knowledge about AI could have modulated the relationship between their attitudes towards AI and their confidence in their reality judgements.

<!-- Re-exposure Delay -->
Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real. This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural]. Although the distribution variance in re-exposure delay is small, recent research using event-related brain potentials report representations of faces to be qualitatively similar regardless of the degree and type of familiarity (e.g., personal or media-based), only distinguishing between familiar and unfamiliar faces [@wiese2021familiarity]. Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness. Future studies could hence further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.

>>>>

<!-- inter-indiv correlates -->
Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments. Given the negative correlation between honesty-humility and narcissism [@hodson2018dark], we put this result in perspective with the positive link observed with narcissistic acclaim seeking, confirming evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose]. However, an inverse effect was found for other facets of narcissism, such as authoritativeness and thrill seeking. We interpret these effects as related to a higher response assertiveness and, for thrill seeking, tolerance of cognitive uncertainty (note that the tolerance to uncertainty scale, which mostly measures the anxiety associated with uncertain events, did not show any link). Taken together, these results suggest that participants with low humility, high recognition desires, and high excitement-seeking traits are more confident in their judgment regarding the real or fake nature of ambiguous stimuli. Participants with opposite traits might perceive a higher risk in the decision process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.

<!-- AI attitudes -->
Despite the ubiquity of AI, the literature pertaining on the influence of people's AI attitudes on simulation monitoring is scarce. Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions). Instead, we found that one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings. It is possible that participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions. This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].

<!-- Social phobia -->
However, it is to important note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*. In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, which low values were associated with an increased tendency of rating faces as real. **TODO: a bit of discussion, mostly on the fact taht the stimuli used were faces**.

<!-- Re-exposure Delay -->
On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real. This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural]. Although the distribution variance in re-exposure delay is small, recent research using event-related brain potentials report representations of faces to be qualitatively similar regardless of the degree and type of familiarity (e.g., personal or media-based), only distinguishing between familiar and unfamiliar faces [@wiese2021familiarity]. Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness. Future studies could hence further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
